%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% This is the official template for theses and seminar papers from the Chair for Information Systems for Sustainable Society (IS3) at the University of Cologne

%
%PREAMBLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper, oneside, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{rotating}

% set margins for double-sided printing
\usepackage[left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm, bindingoffset=1.5cm, head=15pt]{geometry} 
\usepackage{setspace}
\onehalfspacing
% set headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L,RO]{\textsl{\leftmark}}
\fancyhead[R,LO]{\thesisauthor}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

% set APA citation style

\usepackage{apacite}
\usepackage[numbib,notlof,notlot,nottoc]{tocbibind}
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%THESIS Parameters 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Using discrete event simulation to quantify performance of a car-sharing network with a heterogeneous shared fleet}

\newcommand{\thesisdate}{January 23rd, 2022}
\newcommand{\thesisauthor}{Luca Elias Fanselau} %input name
\newcommand{\studentID}{7369806} %input student ID
\newcommand{\thesistype}{Seminar Paper} % Set either to Bachelor or Master
\newcommand{\supervisor}{Univ.-Prof. Dr. Wolfgang Ketter}
\newcommand{\cosupervisor}{Muhammed Demircan}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%DOCUMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%TITLE PAGE (Pre-defined, just change parameters above)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Template/Title.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%SOOA
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Template/SOOA.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\thispagestyle{empty}
\section*{Abstract}


In the rapidly growing market of car-sharing mobility, operational decision-making
can determine success or failure for car-sharing organizations. Predicting the impact
of these decisions analytically is a complex and high dimensional problem. Further complexity
comes from the heterogeneity of the vehicle fleet a customer is offered.
This paper proposes
a discrete event simulation that aims to provide quantitative metrics,
indicating the performance of the car-sharing networks and therefore providing a computationally
efficient way to analyze the effect of operational decisions. The simulation environment models a non-floating
one-way car-sharing system, equipped with a vehicle choice classifier that
is trained using existing car-sharing rental data. The classifier receives a customer request as input,
that is defined by socio-demographic factors as well as the planned route.
The proposed framework is then implemented for a specific car-sharing deployment in Berlin, Germany.
The dynamics of the model, in terms of the presented metrics,
are then analyzed in regard to the fleet size as well as the substitution effect, that
captures the choice uncertainty when selecting a specific vehicle type
that is typically present in real-world
decision-making. 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%TOC,TOF,TOT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\pagenumbering{Roman}
\tableofcontents
\clearpage
\listoffigures
\clearpage
\listoftables

\section*{List of Symbols}

\begin{tabularx}{\linewidth}{lX}
    $C$ & Parameter of the simulation model. Represents the maximum capacity of each vehicle class at each station \\
    $\alpha$ & Parameter of the simulation model. Represents the substitution effect. \\
    $\mathbb{C}$ & The set of all vehicle class choices \\
    $\mathbb{R}$ & The set of all real numbers \\
    $\mathbb{N}$ & The set of all natural numbers \\
    $cost$ & Function that maps the class and rental time to a price \\
    $\mathbb{X}$ & Set of socio-demographic categories that define an area \\
    $a$ & A specific area in regard to the categories $\mathbb{X}$ \\
    $\mathbb{S}$ & Set of all stations in the simulation \\
    $\mathbb{E}$ & Set of all connecting edges of the graph that is formed by $\mathbb{S}$ \\
    $L: \mathbb{E} \to \mathbb{R}$ & Distance mapping for each edge \\
    $\Delta_s$ & The delta function of a station. Indicates the number of vehicles of each type that is rented up until a specific simulation time. Always greater than $-C$\\
    $r$ & A customer request, containing a start station $s_{r, 0}$ and an end station $s_{r, 1}$ \\
    $D$ & A function that returns the set of all feasible vehicle choices for a request, with regard to the substitution effect \\
    $D'$ & Restricted subset of $D$ that checks availability of the vehicle type at $s_{r, 0}$ \\
    $URR$ & Unsatisfied Request Ratio \\
    $\pi$ & The total profit of the simulation stage \\
    $TD$ & The total distance driven during the simulation stage \\
\end{tabularx}


\clearpage

\pagenumbering{arabic}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%MAIN PART
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Introduction
\input{./Sections/Introduction}

% Literature Review
\input{./Sections/LiteratureReview}

% Methods
\input{./Sections/Method}

% Case Study
\input{./Sections/CaseStudy}

% Simulation
% \input{./Sections/Simulation}

% Vehicle Choice Model
% \input{./Sections/VehicleChoice}

% Results & Discussion
\input{./Sections/Results}

% Conclusion
\input{./Sections/Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\appendix
\renewcommand*{\thesection}{\Alph{section}}\textbf{}

% APPENDIX A
\input{Appendices/Appendix_1.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\renewcommand*{\thesection}{}\textbf{}

\bibliographystyle{apacite}
\bibliography{Bibliography.bib}


\end{document}
